---
title: "Lab 5"
author: "Anna Zauner"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence intervals

In this section, we'll use the `t.test()` funciton to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then use `t.test()` to return C.I., and learn about in-line code referencing so out text becomes more reproducible, too.


```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# ?t.test to see what values are included in test in order
# to call elements from list: objectname$valuename


# Find the standard deviation

otter_sd <- sd(otter_lengths)


```

Confidence interval means: If we took multiple samples from population and calculated C.I.s for them then, in 95% of the confidence intervals you would expect to find the true population mean. 

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8), with a 95% confidence interval of [29.1, 44.7] inches.

Problem - because not reducible 

#### Now using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [r round(otter_ci$conf.int[1], 1), round(otter_ci$conf.int[2], 1)`] inches. 

## Part 2: Two-sample t-test

### Example 1

Make two mock samples, and ask the questions: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populationns with the same mean?

```{r}
# make mock samples

oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)

pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# two-sample t-test

tree_t <- t.test(oak_trees, pine_trees)

# Null hypothesis; mean heights are the same
# i.e. : Trees are drawn from populations with the same mean height
```

P-value means: The probability that trees are drawn from populations with the same mean height, the two random samples have this difference in sample means or less, is a 28% chance if taken at random. (start with null hypothesis)

"If these populations have the same mean height, there is a 28% change of taking two random sample with sample means at least this different taken at random."

Therefore, not enough evidence to reject null hypothesis. 

The mean heights of oak and pine trees were (X +/- Y) and (X +/- Y), respectively and the difference was not significant (t(`r round(tree_t$parameter, 1)`) = `r round(tree_t$statistic, 1)`, p = `r round(tree_t$p.value, 1)`)

"t(df) = t-statistic, p = p-value)"

*AVOID* p = 0

when things get really small ( usually p< 0.001)

## Part 3: Another t-test with cars data

Using the `mpg` dataset

### Take a look at the data

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

# check for remaining levels

unique(compact_suv$class)

```

Create a histogram of city gas mileage (city) faceted by class starting from compact_suv

```{r}

ggplot(data = compact_suv, aes(x = cty))+
  geom_histogram(bins = 12, fill = "blue")+
  facet_wrap(~class)

ggplot(data = compact_suv, aes(sample = cty))+
  geom_qq()+
  facet_wrap(~ class)


```
Grey area justification : given central limits theorem, given t-test and qq test both telling me...therefore.. appropriate way to compare means with t-test


Find some summary statistics for each group

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = round(mean(cty), 2),
    sd_city = round(mean(cty), 2),
    sample_size = n()
  )

car_stats
```
The t.test() function REALLY wants vectors of things. Use the `pull()` function to pull our a vector from a data frame.

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
  
```


Mean city gas mileages for SUVs and compact cars are the same. 

```{r}
t.test(compact_sample, suv_sample)

```

What p-value means: If these populations have the same mean gas mileage, there is a 0.0000000022% chance that two random samples have a mean differece of at least 11.393. Therefore, reject the null hypotheses, very unlikely that these are drawn from populations with the same mean gas mileage. There is a significant difference in mean city gas mileage for suvs and compact cars (t(df) = t-statistic, p < 0.001).
