---
title: "Lab 5"
author: "Anna Zauner"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence intervals

In this section, we'll use the `t.test()` funciton to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then use `t.test()` to return C.I., and learn about in-line code referencing so out text becomes more reproducible, too.


```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# ?t.test to see what values are included in test in order
# to call elements from list: objectname$valuename


# Find the standard deviation

otter_sd <- sd(otter_lengths)


```

Confidence interval means: If we took multiple samples from population and calculated C.I.s for them then, in 95% of the confidence intervals you would expect to find the true population mean. 

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8), with a 95% confidence interval of [29.1, 44.7] inches.

Problem - because not reducible 

#### Now using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches.  


